---
output:
  html_document:
    theme: null
    mathjax: null
---

Statistical methods that have been applied to two-group DE of RNA-seq data are widely different in terms of their assumptions on data distribution, input/output format, performance, sensitivity, and user-friendliness, which are summarized in the table below:

```{r include=FALSE}
require(knitr);
require(DEGandMore); 
require(awsomics); 
data("DeMethodMeta");

tbl <- data.frame(Name=DeMethodMeta[[1]], Call=rownames(DeMethodMeta), DeMethodMeta[, 2:9], stringsAsFactors = FALSE);
tbl[[1]] <- AddHref(tbl[[1]], DeMethodMeta$Link); 
```

<div style="color:darkblue; padding:0 0cm;">
**Table 1** Analysis methods for differential expression. 

Column description: 

  - **Name**: Method names to be showed on the web portal.
  - **Call**: The names of the re-implemented functions in the [DEGandMore](http://github.com/zhezhangsh/DEGandMore) package. 
  - **Default**: An arbitrarily selected popular DE methods.
  - **Speed**: How much time the DE method takes to finish. Typically, _fast_ methods take a few seconds, _medium_ methods take up to a minute, and _slow_ methods take a few minutes or more. Therefore, the waiting time will be long if any _slow_ methods are selected.
  - **Paired**: Whether the method supports paired test.
  - **Logged**: Wehther the original method is performed on transformed data in logged scale.
  - **Normalization**: Whether the method has its own internal normalization procedure. 
  - **Distribution**: Which data distribution the original method is based upon. 
  - **Test**: The statistical test used by the method. 
  - **Function**: The main function and package within which the method was originally implemented. 
</div>

<div style="padding:0 0cm;">
```{r echo=FALSE, results='asis'}
kable(tbl, row.names = FALSE, format = 'markdown');
```
</div>

