---
output:
  html_document:
    theme: null
    mathjax: null
---

All DE methods available through **RNAseq 2G** report a 6-column table of test statistics. All tables from the same analysis will have the same size and the same number and order of row and column names. The rows are the genes of read count matrix, after filtering for missing values and low read count.

<div style="color:darkblue; padding:0 0cm;">
**Table 2** Example of analysis output from all DE methods, a 6-column table:

Column description: 

  - **Mean_Control** and **Mean_Patient** The group means of normalized read counts, using the internal normalization of the DE method or user-specified normalization if the method doesn't have one. If the DE method uses log-transformed data, the final values in these columns will be un-logged.
  - **Patient-Control**: The different between the first 2 columns. 
  - **LogFC**: The log2-ratio of group means, which is often refered to as _fold change_. For example, when the average read counts of the two groups is 1:4, the log2-ratio equals to 2.0; and when the ratio is 8:1, the log2-ratio will be -3.0. If a DE method has no its own algorithms to calculate log2-ratios, the values will be calculated based on normalized data. Missing values will be replaced with 0. 
  - **Pvalue**: The statistical significance of group difference. This is the column that differs all DE methods as each method has its own assumption about data distribution and choice of statistical test. Missing values in the original result will be replaced by 1.0 in the final table. **RNA-seq 2G** provides online visualization to compare p values from different DE methods side-by-side. 
  - **FDR**: False discovery rate calculated from the p value using the _Benjamini-Hochberg_ method. Although some DE methods also calculate FDRs or other adjusted p values using their own algorithms, they will not be used in this table. Therefore, the values in this column is solely based on the ***Pvalue*** column and calculated the same way for all DE methods. 
</div>

```{r include=FALSE}
require(knitr);
require(DEGandMore); 
require(awsomics); 
data("DeMethodMeta");
```
<div align="center", style="padding:0 1cm;"> 
```{r echo=FALSE, results='asis'}
data(result_example);
tbl <- FormatNumeric(result_example[[2]][[1]][1:8, ]);
kable(round(tbl, 2), format = 'markdown', row.names = TRUE, align='r');
```
</div>
